Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/abstraction_notation.tex

%Lihong Section
\section{Abstraction Notation}
We build upon the notation used by \citep{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.

>>>>

%Lihong Section
\section{Abstraction Notation}
We build upon the notation used by \citet{li2006towards}, who introduced a unifying theoretical framework for state abstraction in \acp{MDP} and sequential decision making.

### 2016-02-05 paper/example_domains.tex

% Subsection: Minefield.
\subsection{Minefield}

Minefield is a test problem we are introducing that uses the Grid World dynamics of \citeauthor{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward. (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=1.1, \kappa = 5, x = 0.01$. We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\varepsilon=1.1$}
\end{figure}

>>>>

% Subsection: Minefield.
\subsection{Minefield}
>
Minefield is a test problem we are introducing that uses the Grid World dynamics of \citeauthor{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward. (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$. We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.

% Minefield Compression Visuals
\begin{figure}
\subfigure[Ground Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.48\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\varepsilon=0.5$}
\end{figure}

### 2016-02-05 paper/results_discussion.tex

\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\subfigure[Minefield]{
\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\subfigure[Random]{
\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
\caption{$\varepsilon$ vs. Num States and $\varepsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
\end{figure*}

>>>>

\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy.pdf}
}
\subfigure[Minefield]{
\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_value_of_abstract_policy.pdf}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_value_of_abstract_policy.pdf}
}
\subfigure[Random]{
\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_value_of_abstract_policy.pdf}
}
\caption{$\varepsilon$ vs. Num States and $\varepsilon$ vs. Abstract Policy Value\label{fig:main_empirical_results1}}
\end{figure*}
